\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-14 paper.tex
updated abstract

We present a new methodology for systematically testing distributed systems. Our approach involves the use of \psharp, an extension of \csharp that combines a flexible environmental modeling approach with a concurrency testing framework, which can capture and systematically explore all sources of nondeterminism \SCComment{this paper mainly focuses on the nondet due to scheduling, right? There are other sources, e.g., arbitrary input, system call behavior, clock, random number, etc. I feel that ``all sources'' is perhaps an overclaim} \PDComment{We should clarify: as long as you model a source of nondet using \psharp, then you can capture it and control it (not automatically)}. We present two case studies of using \psharp to test production distributed systems inside Microsoft. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time, as they did not have an effective way to reproduce it. \psharp uncovered the bug in a very small setting, which made it easy to examine traces, identify and fix the problem. \PDComment{we now have many bugs in Matt's system too.}

>>>>

We discuss our experience of using \psharp inside Microsoft to test three distributed storage systems for the Windows Azure cloud computing platform. \psharp is an extension of the \csharp language that provides environmental modeling capabilities and a systematic concurrency testing engine. As long as the developer has expressed all sources of nondeterminism in a system using \psharp, then the \psharp testing engine can systematically explore all these sources of nondeterminism to find bugs.

The power of \psharp is that it enables the developer to \emph{test what is being executed} and is engineered to work on production-level code. Using \psharp we managed to find and reproduce more than 10 hard-to-find with traditional testing techniques bugs in our case studies. As an example, \psharp found a very subtle bug that was haunting developers for a long time, as they did not have an effective way to reproduce it. \psharp uncovered the bug in a very small setting, which made it easy to examine traces, identify and fix the problem.
